\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-06-01 doc/sw-system.tex
All crowd figs are in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
\caption{Narrow cumulutive distributions of the contributions made by the
agents: for example, 90\% of the stage 2 contributions were made by the
highest contributing  7\% of the crowd. The stage 1 agents are shown in blue,
the stage 2 agents in orange. ``Experienced volunteers'' classified 10 or more
training subjects.}
\label{fig:crowd:cumulplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.png}
\caption{Broad cumulutive distributions of agent skill: 
the most skilled 20\% of the crowd only possess 79\% of the skill at stage 1.
The stage 1 agents
are shown in blue, the stage 2 agents in orange. ``Experienced volunteers''
classified 10 or more training subjects.}
\label{fig:crowd:cumulskillplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Can we predict skill? Early skill vs final skill - some correlation,
especially in high skill users, but very broad distribution though: not
possible to predict.
\Fref{fig:crowd:skillprediction}

Stage 1 skill vs Stage 2 skill. 
Who continued to do Stage 2? Numbers. 
\Fref{fig:crowd:stage1vstage2}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
\caption{Narrow cumulative distributions of the contributions made by the
agents: for example, 90\% of the stage 2 contributions were made by the
highest contributing  7\% of the crowd. The stage 1 agents are shown in blue,
the stage 2 agents in orange. ``Experienced volunteers'' classified 10 or more
training subjects.}
\label{fig:crowd:cumulplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.png}
\caption{Broad cumulative distributions of agent skill: 
the most skilled 20\% of the crowd only possess 79\% of the skill at stage 1.
The stage 1 agents
are shown in blue, the stage 2 agents in orange. ``Experienced volunteers''
classified 10 or more training subjects.}
\label{fig:crowd:cumulskillplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
\caption{Stage 2 agent properties, separating veterans from stage 1 from new
volunteers. Point size represents total information generated, dashed lines
are drawn at the mean values for each sample.}
\label{fig:crowd:stage1vstage2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We now look at the transition between stage 1 and stage 2 in more detail. Of
the 1964 volunteers who took part in the stage 2 classification round, only
783 were veterans from stage 1. However, these volunteers showed significantly
higher skill levels than the new users, and also made more classifications
(and hence made greater contributions. This is illustrated in  
\Fref{fig:crowd:stage1vstage2}. In this figure, point size is proportional to
information generated: the higher skill, higher effort stage 1 veterans
generated most of the information.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
\caption{Predictability of final skill from early skill (after 10 training
classifications) in stage 1 agents. The dashed lines enclose 649 agents with
early skill greater than 0.1 
who retain final skill of greater than 0.05.}
\label{fig:crowd:skillprediction}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Having seen the importance of the high skill volunteers at both stage 1 and
stage 2, we might ask, can we predict agent skill after, say, the volunteer
has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
plot this ``early skill'' against final skill, for all experienced stage 1
volunteers. The majority of the crowd shows little correlation, but at the
high early skill end, some predictability appears. The 649 experienced  stage
1 volunteers who had early skill greater than 0.1 went on to attain a mean
final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
suggests that it might be worth tracking volunteers' skill as a project
progresses, in order to encourage those showing an aptitude for the task to
take part in the more difficult activities, such as stage 2 refinement.

@@
